SVG: The Paper

### 2022-04-14 Analysis/index.Rmd
more anal

```{r, fig.cap = "Accuracy of our model varies with the strength of an individual's proximity bias."}
# computed in xxxx.R
fit <- readRDS("scratch/qjep_model_fit.rda") %>%
  full_join(a_acc, by = c("observer", "condition"))

ggplot(fit, aes(bP, accuracy, colour = condition)) + 
  geom_point() +
  geom_smooth(method = "lm", formula = y ~ x, se = FALSE)
```
Furthermore, this appears to account for most of the difference between the *feature* and *conjunction* conditions.

```{r, echo = TRUE}
summary(lm(accuracy ~ condition * bP, fit))
```
### Examples of Trials

@@

```{r, echo = TRUE}
a %>% group_by(observer, condition, trial) %>% 
  summarise(prop_max = mean(selected_max), .groups = "drop") %>% 
  arrange(desc(prop_max)) %>%
  ungroup() -> a_trl
```

@@

```{r fig.cap = "A random selection of *good* trials."}
plts <- map(1:3, plot_trial, trls_easy, a, d)

@@

Here are some typical trials. Possible we have the path-length minimisation issue again.

```{r fig.cap = "A random selection of *typical* trials."}
plts <- map(1:3, plot_trial, trls_mid, a, d)

@@

Now let's look at less predictable trials:

```{r fig.cap = "A random selection of *hard* trials."}
plts <- map(1:3, plot_trial, trls_hard, a, d)

>>>>

```{r, fig.cap = "Accuracy of our model varies with the strength of an individual's model parameters. We can see two clear outlier participants (marked with an X). "}
# computed in xxxx.R
fit <- readRDS("scratch/qjep_model_fit.rda") %>%
  full_join(a_acc, by = c("observer", "condition")) %>%
  mutate(is_outlier = if_else(observer %in% c(35, 45), TRUE, FALSE))

fit_plt <- pivot_longer(fit, c(pA, pS, bP, bM), 
                     names_to = "parameter", values_to = "value")

ggplot(fit_plt, aes(value, accuracy, colour = condition)) + 
  geom_point(aes(shape = is_outlier)) +
  geom_smooth(data = filter(fit_plt, is_outlier == 0), method = "lm", formula = y ~ x, se = FALSE) + 
  scale_shape_manual(values = c(19, 4), guide = "none") + 
  facet_wrap(~parameter, scales = "free") +
  theme(legend.position = "bottom")
```
As the two outlier participants appear to be doing something different, not captured especially well by our model, we will remove them from the rest of this analysis.

After removing them, we can see that individual differences in proximity tuning account for nearly all of the differences in predictability from person to person, and also between the *feature* and *conjunction* conditions.

```{r, echo = TRUE}
summary(lm(accuracy ~ condition * bP, 
           data = filter(fit, is_outlier == 0)))

summary(lm(accuracy ~ bP + pS + bM + bP, 
           data = filter(fit, is_outlier == 0)))

```

### Examples of Trials

@@

```{r, echo = TRUE}
a %>% filter(!(observer %in% c(35, 45))) %>%
  group_by(observer, condition, trial) %>% 
  summarise(prop_max = mean(selected_max), .groups = "drop") %>% 
  arrange(desc(prop_max)) %>%
  ungroup() -> a_trl
```

@@

```{r fig.cap = "A random selection of *good* trials. When participants diverge from the model's prediction, it appears to be due to some form of path-length optimisation."}
plts <- map(1:3, plot_trial, trls_easy, a, d)

@@

Here are some typical trials. Possible we have the path-length minimization issue again.

```{r fig.cap = "A random selection of *typical* trials. Along with path-minimising behaviour, we can also see some disagreement around switching item type."}
plts <- map(1:3, plot_trial, trls_mid, a, d)

@@

Now let's look at less predictable (bottom 5%-tile) trials. Even here, the model does a relatively good job.

```{r fig.cap = "A random selection of *hard* trials. It is harder to make out much of a pattern here, but we can see that the human participants jump around more."}
plts <- map(1:3, plot_trial, trls_hard, a, d)
